---
title: "Trajectories"
author: "Zachary"
date: '2025-07-28'
output: html_document
---

# Library & Notes
```{r setup, include=FALSE}
library(haven); library(dplyr); library(tidyr); library(readr); library(readxl); library(data.table); library(stringr); library(purrr)  # Data manipulation & import
library(lme4); library(lmerTest); library(coxme); library(survival); library(broom); library(MuMIn); library(lsmeans)  # Modeling & statistics
library(pander); library(apaTables); library(flextable); library(officer); library(webshot2)  # Tables & reporting
library(ggplot2)  # Plotting
library(fuzzyjoin)  # Joins
library(survminer)
#library(hexbin)
#library(pwr)
```

#Power Analysis




#Graph

## Load Analytic & Sleep
```{r}
setwd("C:/Users/hubshmz/Documents/Code/git/data")  # FORBOW computer
# setwd("C:/Users/zachh/Documents/Code/git/Data")  # Laptop
# setwd("C:/Users/zacha/Documents/RStudio/forbow/git/Data") # Tupper Windows Comp
# setwd("C:/Users/zacha/Documents/forbow/code/git") # Home Computer

load("analytic-zach.RData")
Night <- read.csv("part4_summary_sleep_cleaned.csv")
```
### Actigraphy
## Check total valid amount of participants
```{r}
Night <- Night %>% filter(n_WE_nights_complete >= 3 & n_WD_nights_complete >= 1)


Night$Subject_ID <- substr(Night$filename, 1, 12)
Night$Assessment_Date <- str_extract(Night$filename, "\\d{4}-\\d{2}-\\d{2}")
Night <- Night %>% 
  filter(!str_detect(filename, "F[1-3]|f[1-3]|M[1-3]|m[1-3]|\\$R"))


bin_files_to_remove <- c(
  "8000103174_left wrist_068158_2025-06-03 10-40-36.bin",
  "8000156273_left wrist_060381_2024-11-05 12-04-08_partial.bin",
  "8000156273_left wrist_060381_2024-11-05 12-27-40.bin",
  "800304581_right wrist_060843_2024-11-05 13-16-09.bin",
  "800304582__060365_2024-11-05 12-03-44.bin",
  "800304582__060365_2024-11-05 12-28-01.bin"
)

Night <- Night %>%
  filter(!filename %in% bin_files_to_remove)
Night <- Night %>%
  mutate(Subject_ID = gsub("^800-(\\d{3})-(\\d+)_$", "800-0\\1-\\2", Subject_ID))

Night$Subject_ID <- gsub("-", "", Night$Subject_ID)
Night$Subject_ID <- gsub("[a-zA-Z]", "", Night$Subject_ID)
Night$Subject_ID <- gsub("_", "", Night$Subject_ID)
FOR$Subject_ID <- gsub("-", "", as.character(FOR$subject_id))
```

```{r}
setDT(Night)
setDT(FOR)

Night[, Assessment_Date := as.Date(Assessment_Date)]
FOR[, Assessment_Date := as.Date(assessment_date)]
#Perform a left join, retaining all rows in day4merge
##Performing merge, making day4days, but this only merges individuals who actually have a subject_ID and assessment_date
setorder(Night, Subject_ID, Assessment_Date)
setorder(FOR, Subject_ID, Assessment_Date)
merged <- FOR[Night, on = .(Subject_ID, Assessment_Date), roll = "nearest"]
```

#Mean Graphing
Used generalized additive model 
```{r}
merged$RoundAge <- round(merged$age)
merged$group <- factor(merged$group,
                       levels = c(0, 1, 2, 3),
                       labels = c("Control", "MDD Risk", "BD Risk", "Psy Risk"))
merged$sex <- factor(merged$sex,
                       levels = c(0, 1),
                       labels = c("Male", "Female"))
merged <- merged %>% filter(group != 3)
merged <- merged %>% 
  filter(!is.na(group))
merged %>%
  filter(group != 3)
```

##Sleep Regularity Index
```{r}
a_f_WD <- ggplot(data = merged, mapping = aes(x = age, y = SleepRegularityIndex1_WD_T5A5_mn, color = group)) +
  geom_point(alpha = 0.6, size = 3) +
  geom_smooth(method = "gam", aes(group = group), se = FALSE, linetype = "solid", size = 1) +
  scale_color_brewer(palette = "Dark2") +  
    scale_y_continuous(
    limits = c(10, 90),
    breaks = seq(10, 90, by = 10)
  ) +
  labs(
    title = "Sleep Regularity Index Across Age by Group Weekdays (Faceted)",
    x = "Age",
    y = "Sleep Regularity Index",
    color = "Group"
  ) + facet_wrap(~ group)
a_f_WD

a_f_WE <- ggplot(data = merged, mapping = aes(x = age, y = SleepRegularityIndex1_WE_T5A5_mn, color = group)) +
  geom_point(alpha = 0.6, size = 3) +
  geom_smooth(method = "gam", aes(group = group), se = FALSE, linetype = "solid", size = 1) +
  scale_color_brewer(palette = "Dark2") +  
      scale_y_continuous(
    limits = c(10, 90),
    breaks = seq(10, 90, by = 10)
  ) +
  labs(
    title = "Sleep Regularity Index Across Age by Group Weekends (Faceted)",
    x = "Age",
    y = "Sleep Regularity Index",
    color = "Group"
  ) + facet_wrap(~ group) 
a_f_WE
```


##Time Spent Inactive During Sleep Window
```{r}
b_f_WD <- ggplot(data = merged, mapping = aes(x = RoundAge, y = SleepDurationInSpt_WD_T5A5_mn, color = group)) +
  geom_point(alpha = 0.6, size = 3) +
  geom_smooth(method = "gam", aes(group = group), se = FALSE, linetype = "solid", size = 1) +
  scale_color_brewer(palette = "Dark2") + 
    scale_y_continuous(
    limits = c(5, 10),
    breaks = seq(5, 10, by = 1)
  ) +
  labs(
    title = "Sleep Duration Across Age by Group Weekdays (Faceted)",
    x = "Age",
    y = "Sleep Duration (Hours)",
    color = "Group"
  ) + facet_wrap(~ group)
b_f_WD

b_f_WE <- ggplot(data = merged, mapping = aes(x = RoundAge, y = SleepDurationInSpt_WE_T5A5_mn, color = group)) +
  geom_point(alpha = 0.6, size = 3) +
  geom_smooth(method = "gam", aes(group = group), se = FALSE, linetype = "solid", size = 1) +
  scale_color_brewer(palette = "Dark2") + 
    scale_y_continuous(
    limits = c(5, 10),
    breaks = seq(5, 10, by = 1)
  ) +
  labs(
    title = "Sleep Duration Across Age by Group Weekends (Faceted)",
    x = "Age",
    y = "Sleep Duration (Hours)",
    color = "Group"
  ) + facet_wrap(~ group)
b_f_WE
```

##Total Sleep Window Time
```{r}
#WeekDay 
c_f_WD <- ggplot(data = merged, aes(x = RoundAge, y = SptDuration_WD_T5A5_mn, color = group)) +
  geom_point(alpha = 0.6, size = 3) +
  geom_smooth(method = "gam", aes(group = group), se = FALSE, linetype = "solid", size = 1) +
  scale_color_brewer(palette = "Dark2") +
    scale_y_continuous(
    limits = c(6, 12)) + 
  labs(
    title = "Time in Bed and Age by Group Weekday (Faceted)",
    y = "Time in Bed",
    x = "Age",
    color = "Group"
  ) +
  facet_wrap(~ group)
c_f_WD

#Weekend
c_f_WE <- ggplot(data = merged, aes(x = RoundAge, y = SptDuration_WE_T5A5_mn, color = group)) +
  geom_point(alpha = 0.6, size = 3) +
  geom_smooth(method = "gam", aes(group = group), se = FALSE, linetype = "solid", size = 1) +
  scale_color_brewer(palette = "Dark2") +
    scale_y_continuous(
    limits = c(6, 12)) + 
  labs(
    title = "Time in Bed and Age by Group Weekend (Faceted)",
    y = "Time in Bed",
    x = "Age",
    color = "Group"
  ) +
  facet_wrap(~ group)
c_f_WE
```

##Sleep Onset
```{r}
#Weekday
d_f_WD <- ggplot(data = merged, mapping = aes(x = age, y = sleeponset_WD_T5A5_mn, color = group)) +
  geom_point(alpha = 0.6, size = 3) +
  geom_smooth(method = "gam", aes(group = group), se = FALSE, linetype = "solid", size = 1) +
  scale_color_brewer(palette = "Dark2") + 
  scale_y_continuous(
    limits = c(20, 28),
    breaks = seq(20, 28, by = 2)
  ) +
  labs(
    title = "Sleep Onset Age by Group Weekdays (Faceted)",
    x = "Age",
    y = "Sleep Sleep Onset (Hours, 24 is Midnight)",
    color = "Group"
  ) +
  facet_wrap(~ group)
d_f_WD

#Weekend
d_f_WE <- ggplot(data = merged, mapping = aes( x = age, y = sleeponset_WE_T5A5_mn, color = group)) +
  geom_point(alpha = 0.6, size = 3) +
  geom_smooth(method = "gam", aes(group = group), se = FALSE, linetype = "solid", size = 1) +
  scale_color_brewer(palette = "Dark2") + 
  scale_y_continuous(
    limits = c(20, 28),
    breaks = seq(20, 28, by = 2)
  ) +
  labs(
    title = "Sleep Onset Age by Group Weekends (Faceted)",
    x = "Age",
    y = "Sleep Sleep Onset (Hours, 24 is Midnight)",
    color = "Group"
  ) +
  facet_wrap(~ group)
d_f_WE
```

##Sleep Wakeup
```{r}
#Weekday
e_f_WD <- ggplot(data = merged, aes(x = age, y = wakeup_WD_T5A5_mn, color = group)) +
  geom_point(alpha = 0.6, size = 3) +
  geom_smooth(method = "gam", aes(group = group), se = FALSE, linetype = "solid", size = 1) +
  scale_color_brewer(palette = "Dark2") +
    scale_y_continuous(
    limits = c(28, 36),
    breaks = seq(28, 36, by = 2)
  ) +
  labs(
    title = "Sleep Wakeup and Age by Group Weekdays (Faceted)",
    y = "Sleep Wakeup (Hours)",
    x = "Age",
    color = "Group"
  ) +
  facet_wrap(~ group)
e_f_WD

#Weekend
e_f_WE <- ggplot(data = merged, aes(x = age, y = wakeup_WE_T5A5_mn, color = group)) +
  geom_point(alpha = 0.6, size = 3) +
  geom_smooth(method = "gam", aes(group = group), se = FALSE, linetype = "solid", size = 1) +
  scale_color_brewer(palette = "Dark2") +
    scale_y_continuous(
    limits = c(28, 36),
    breaks = seq(28, 36, by = 2)
  ) +
  labs(
    title = "Sleep Wakeup and Age by Group Weekend (Faceted)",
    y = "Sleep Wakeup (Hours)",
    x = "Age",
    color = "Group"
  ) +
  facet_wrap(~ group)
e_f_WE
```


##WASO
```{r}
f_f_WD <- ggplot(data = merged, aes(x = age, y = WASO_WD_T5A5_mn, color = group)) +
  geom_point(alpha = 0.6, size = 3) +
  geom_smooth(method = "gam", aes(group = group), se = FALSE, linetype = "solid", size = 1) +
  scale_color_brewer(palette = "Dark2") +
    scale_y_continuous(
    limits = c(0, 3),
    breaks = seq(0, 3, by = 1)
  ) +
  labs(
    title = "WASO and Age by Group Weekdays (Faceted)",
    y = "WASO",
    x = "Age",
    color = "Group"
  ) +
  facet_wrap(~ group)
f_f_WD

#weekend
f_f_WE <- ggplot(data = merged, aes(x = age, y = WASO_WE_T5A5_mn, color = group)) +
  geom_point(alpha = 0.6, size = 3) +
  geom_smooth(method = "gam", aes(group = group), se = FALSE, linetype = "solid", size = 1) +
  scale_color_brewer(palette = "Dark2") +
    scale_y_continuous(
    limits = c(0, 3),
    breaks = seq(0, 3, by = 1)
  ) +
  labs(
    title = "WASO and Age by Group Weekend (Faceted)",
    y = "WASO",
    x = "Age",
    color = "Group"
  ) +
  facet_wrap(~ group)
f_f_WE
```

#Non-Mean Exploration
```{r}
rm(list = ls())
# setwd("C:/Users/hubshmz/Documents/Code/git/data")  # FORBOW computer
setwd("C:/Users/zachh/Documents/Code/git/Data")  # Laptop
# setwd("C:/Users/zacha/Documents/RStudio/forbow/git/Data") # Tupper Windows Comp
# setwd("C:/Users/zacha/Documents/forbow/code/git") # Home Computer

FOR <- read.csv("FOR.csv")  
Night <- read.csv("part4_nightsummary_sleep_cleaned.csv")
NightM <- read_excel("motionloggerdata.xlsx")

Night$Subject_ID <- substr(Night$filename, 1, 12)
Night$Assessment_Date <- str_extract(Night$filename, "\\d{4}-\\d{2}-\\d{2}")
Night <- Night %>% 
  filter(!str_detect(filename, "F[1-3]|f[1-3]|M[1-3]|m[1-3]|\\$R"))


bin_files_to_remove <- c(
  "8000103174_left wrist_068158_2025-06-03 10-40-36.bin",
  "8000156273_left wrist_060381_2024-11-05 12-04-08_partial.bin",
  "8000156273_left wrist_060381_2024-11-05 12-27-40.bin",
  "800304581_right wrist_060843_2024-11-05 13-16-09.bin",
  "800304582__060365_2024-11-05 12-03-44.bin",
  "800304582__060365_2024-11-05 12-28-01.bin"
)

Night <- Night %>%
  filter(!filename %in% bin_files_to_remove)
Night <- Night %>%
  mutate(Subject_ID = gsub("^800-(\\d{3})-(\\d+)_$", "800-0\\1-\\2", Subject_ID))

Night$Subject_ID <- gsub("-", "", Night$Subject_ID)
Night$Subject_ID <- gsub("[a-zA-Z]", "", Night$Subject_ID)
Night$Subject_ID <- gsub("_", "", Night$Subject_ID)
FOR$Subject_ID <- gsub("-", "", as.character(FOR$subject_id))

setDT(Night)
setDT(FOR)

Night$geneactiv <- 1
FOR[, Assessment_Date := as.Date(assessment_date)]
FOR$Assessment_Date_FOR <- FOR$Assessment_Date
Night[, Assessment_Date := as.Date(Assessment_Date)]  # redundant if already Date
Night$Assessment_Date_Night <- Night$Assessment_Date

# Perform the join with date window logic
merged1 <- Night[FOR, on = .(Subject_ID), allow.cartesian = TRUE]

merged1[, diffdays := abs(as.numeric(difftime(Assessment_Date_Night, Assessment_Date_FOR, units = "days")))]

merged1 <- merged1 %>% filter(diffdays <= 179)

two <- merged1[(Subject_ID %in% c(8000038204, 8000114479))]



NightM$weekday <- NightM$eday
NightM <- NightM %>% 
  filter(!str_detect(Subject_ID, "F[1-3]|f[1-3]|M[1-3]|m[1-3]|\\$R"))
setDT(NightM)
NightM[, Assessment_Date := as.Date(sdate)]
NightM$Assessment_date_nightM <- NightM$Assessment_Date
merged2 <- NightM[FOR, on = .(Subject_ID), allow.cartesian = TRUE]
merged2[, diffdays := abs(as.numeric(difftime(Assessment_date_nightM, Assessment_Date_FOR, units = "days")))]
merged2 <- merged2 %>% filter(diffdays <= 179)
merged2$motionlogger <- 1



merged <- rbindlist(list(merged1, merged2), fill = TRUE)

#SptDuration#SptDmotionloggeruration
#sleepwakeup
#sleeponset
#WASO
```

#Non-Mean Graphing
```{r}
merged$group <- factor(merged$group,
                       levels = c(0, 1, 2, 3),
                       labels = c("Control", "MDD Risk", "BD Risk", "Psy Risk"))
merged$sex <- factor(merged$sex,
                       levels = c(0, 1),
                       labels = c("Male", "Female"))
merged <- merged %>% 
  filter(!is.na(group))


merged <- merged %>%
  filter(group != 3)

unique_data <- unique(merged[, c("subject_id", "group")])

group_table <- table(unique_data$group)
pander(group_table)


unique_data <- unique(merged1[, c("subject_id", "group")])

group_table <- table(unique_data$group)
pander(group_table)

unique_data <- unique(merged2[, c("subject_id", "group")])

group_table <- table(unique_data$group)
pander(group_table)

pander(table(merged$group))
```

##Sleep Regularity Index
```{r}
a_f_WE <- ggplot(data = merged, aes(x = age, y = SleepRegularityIndex1, color = group)) +
  geom_jitter(alpha = 0.3, width = 0.2, height = 0.5, size = 1.5) +
  geom_smooth(aes(group = group, color = as.factor(group)), method = "gam", se = FALSE, size = 1) +
  scale_color_brewer(palette = "Dark2") +
  scale_y_continuous(limits = c(10, 90), breaks = seq(10, 90, by = 10)) +
  labs(
    title = "Sleep Regularity Index Across Age by Group (Hex Binned + Smooth)",
    x = "Age",
    y = "Sleep Regularity Index",
    fill = "Count",
    color = "Group"
  ) + facet_wrap(~ sex)
a_f_WE



```


##Time Spent Inactive During Sleep Window
```{r}
merged$SleepDurationInSpt <- as.numeric(merged$SleepDurationInSpt)




b_f_WE <- ggplot(data = merged, mapping = aes(x = age, y = SleepDurationInSpt, color = group)) +
  geom_jitter(alpha = 0.1, width = 0.2, height = 0.5, size = 1.2) +
  geom_smooth(
    method = "gam",
    se = FALSE,
    linetype = "solid",
    size = 2,  # thicker
    aes(group = group, color = group)  # reassert color by group for clarity
  ) +
  scale_color_brewer(palette = "Dark2") + 
  scale_y_continuous(
    limits = c(4, 12),
    breaks = seq(4, 12, by = 2)
  ) +
  labs(
    title = "Sleep Duration Across Age by Group All Days (Faceted)",
    x = "Age",
    y = "Sleep Duration (Hours)",
    color = "Group"
  )  +
  theme_minimal()
b_f_WE 

ggplot(merged, aes(x = age, color = group, fill = group)) +
  geom_density(alpha = 0.4) +
  scale_color_brewer(palette = "Dark2") +
  scale_fill_brewer(palette = "Dark2") +
  labs(
    title = "Age Density by Group",
    x = "Age",
    y = "Density",
    color = "Group",
    fill = "Group"
  ) +
  theme_minimal() + facet_wrap(~ group)

merged$day_type <- ifelse(merged$weekday %in% c("Saturday", "Sunday", "Sat", "Sun"), "Weekend", "Weekday")
merged$day_type <- factor(merged$day_type, levels = c("Weekday", "Weekend"))

b_f_WE <- ggplot(data = merged, mapping = aes(x = age, y = SleepDurationInSpt, color = group)) +
  geom_jitter(alpha = 0.1, width = 0.2, height = 0.5, size = 1.2) +
  geom_smooth(
    method = "gam",
    se = FALSE,
    linetype = "solid",
    size = 2,
    aes(group = group, color = group)
  ) +
  scale_color_brewer(palette = "Dark2") + 
  scale_y_continuous(
    limits = c(4, 12),
    breaks = seq(4, 12, by = 2)
  ) +
  labs(
    title = "Sleep Duration Across Age by Group and Day Type",
    x = "Age",
    y = "Sleep Duration (Hours)",
    color = "Group"
  )  +
  facet_grid(day_type ~ group) +   # rows = day type, columns = group
  theme_minimal()
b_f_WE
```
##Extreme sleep duration
```{r}
merged <- merged %>%
  mutate(
    ideal_sleep = case_when(
      age >= 3 & age < 6 ~ 11.5,        # midpoint of 10-13 for Preschool
      age >= 6 & age <= 12 ~ 10.5,      # midpoint of 9-12 for School-age
      age > 12 & age <= 18 ~ 9,         # midpoint of 8-10 for Teen
      age > 18 ~ 7,                     # Adult: 7 or more, midpoint ~7
      TRUE ~ NA_real_                    # for ages outside these ranges
    ),
    sleep_deviation_sq = abs(SleepDurationInSpt - ideal_sleep)
  )

b_fa_WE <- ggplot(data = merged, mapping = aes(x = age, y = sleep_deviation_sq, color = group)) +
  geom_jitter(alpha = 0.1, width = 0.2, height = 0.5, size = 1.2) +
  geom_smooth(
    method = "gam",
    se = FALSE,
    linetype = "solid",
    size = 2,  # thicker
    aes(group = group, color = group)  # reassert color by group for clarity
  ) +
  scale_color_brewer(palette = "Dark2") + 
  scale_y_continuous(
    limits = c(0, 6),
    breaks = seq(0, 6, by = 2)
  ) +
  labs(
  title = "# Of Hours of Sleep Off Recommended",
  x = "Age",
  y = "Absolute Deviation from Recommended Sleep (hours)",
  color = "Group"
)+ theme_minimal()
b_fa_WE 

```

##Total Sleep Window Time
```{r}

#All Days
c_f_WE <- ggplot(data = merged, aes(x = age, y = SptDuration, color = group)) +
  geom_jitter(alpha = 0.1, width = 0.2, height = 0.5, size = 1.2) +
  geom_smooth(method = "gam", aes(group = group), se = FALSE, linetype = "solid", size = 2) +
  scale_color_brewer(palette = "Dark2") +
    scale_y_continuous(
    limits = c(6, 12)) + 
  labs(
    title = "Time in Bed and Age by Group All Days (Faceted)",
    y = "Time in Bed",
    x = "Age",
    color = "Group"
  ) + theme_minimal() 
c_f_WE
```

##Sleep Onset
```{r}

#All Days
d_f_WE <- ggplot(data = merged, mapping = aes( x = age, y = sleeponset, color = group)) +
  geom_jitter(alpha = 0.1, width = 0.2, height = 0.5, size = 1.2) +
  geom_smooth(method = "gam", aes(group = group), se = FALSE, linetype = "solid", size = 2) +
  scale_color_brewer(palette = "Dark2") + 
  scale_y_continuous(
    limits = c(20, 28),
    breaks = seq(20, 28, by = 2)
  ) +
  labs(
    title = "Sleep Onset Age by Group All Days (Faceted)",
    x = "Age",
    y = "Sleep Sleep Onset (Hours, 24 is Midnight)",
    color = "Group"
  ) + theme_minimal() 
d_f_WE


```

##Sleep Wakeup
```{r}

#All Days
e_f_WE <- ggplot(data = merged, aes(x = age, y = wakeup, color = group)) +
  geom_jitter(alpha = 0.1, width = 0.2, height = 0.5, size = 1.2) +
  geom_smooth(method = "gam", aes(group = group), se = FALSE, linetype = "solid", size = 2) +
  scale_color_brewer(palette = "Dark2") +
    scale_y_continuous(
    limits = c(28, 36),
    breaks = seq(28, 36, by = 2)
  ) +
  labs(
    title = "Sleep Wakeup and Age by Group All Days (Faceted)",
    y = "Sleep Wakeup (Hours)",
    x = "Age",
    color = "Group"
  )  + theme_minimal() 
e_f_WE
```


##WASO
```{r}
#weekend
f_f_WE <- ggplot(data = merged, aes(x = age, y = WASO, color = group)) +
  geom_jitter(alpha = 0.1, width = 0.2, height = 0.5, size = 1.2) +
  geom_smooth(method = "gam", aes(group = group), se = FALSE, linetype = "solid", size = 2) +
  scale_color_brewer(palette = "Dark2") +
    scale_y_continuous(
    limits = c(0, 3),
    breaks = seq(0, 3, by = 1)
  ) +
  labs(
    title = "WASO and Age by Group All Days (Faceted)",
    y = "WASO",
    x = "Age",
    color = "Group"
  ) + theme_minimal() 
f_f_WE
```


#power
```{r}
#112 Control
#61 At risk BP
#118 at risk MDD
#19 At risk Psychosis

##Psychosis Test
#131 - 1 - 3(covariates) - 1(dummy group variable)
library(pwr)
pwr.f2.test(u = 1, v = 126, sig.level = 0.01, power = 0.90)


##At risk MDD
pwr.f2.test(u = 1, v = 225, sig.level = 0.01, power = 0.90)

#At risk BP
pwr.f2.test(u = 1, v = 168, sig.level = 0.01, power = 0.90)

```


#Main Analysis


#CSV For
```{r}
# Load into a temporary environment to avoid corrupting your global one
temp_env <- new.env()
load("analytic-zach.RData", envir = temp_env)

# List all objects
all_objs <- ls(temp_env)

# Save each data frame to CSV
for (obj_name in all_objs) {
  obj <- get(obj_name, envir = temp_env)
  
  if (is.data.frame(obj)) {
    # Construct a filename
    filename <- paste0(obj_name, ".csv")
    
    # Write to CSV
    write.csv(obj, file = filename, row.names = FALSE)
    
    message("Saved: ", filename)
  } else {
    message("Skipped (not a data frame): ", obj_name)
  }
}

```
